LAGOS lake depth

### 2019-05-07 lagos_depth.Rmd
add map

```{r message=FALSE}
library(LAGOSNE)
library(ggplot2)
library(sf)
library(dplyr)

@@

```

>>>>

```{r data, message=FALSE}
library(LAGOSNE)
library(ggplot2)
library(sf)
library(dplyr)

@@

ggplot() + 
  geom_sf(data = LAGOSNE::lg_extent) +
  geom_sf(data = dplyr::sample_frac(lg_depth, 0.2), 
          aes(color = cut(maxdepth, round(quantile(maxdepth)))), 
          size = 1, alpha = 0.4, shape = 20) +
  scale_color_viridis_d(direction = -1) +
  coord_sf(datum = NA) + theme_void() +
  labs(color = "depth (m)")
```
